Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-05 paper.tex
spell check and move+tweak tar archive mention

Informal comparison of results from the VISION and Cyclus simulators when
running equivalent scenarios revealed some surprising discrepencies.  One of
the most apparent was a large difference in separated Pu levels between the
two simulators --- something that some in the DOE and nuclear community are
very sensitive to.  For one particular scenario, the Cyclus results also
showed no fuel shortages for reactors, while the VISION results indicated
noticable shortages.  This observation prompted a closer investigation to
determine if the differences were caused by mistakes in simulator input, bugs
in the simulator(s), or differing modeling choices between the simulators.
This investigation eventaully developed into this work which shows important
effects of some modeling choices that are operative in many fuel cycle
simulators.

@@

All results data, analysis tools, and related instructions are publicly
available for download and use at
\url{http://dx.doi.org/10.6084/m9.figshare.1546775} \cite{Carlsen2015}.

@@

>>>>

Informal comparison of results from the VISION and Cyclus simulators when
running equivalent scenarios revealed some surprising discrepancies.  One of
the most apparent was a large difference in separated Pu levels between the
two simulators --- something that some in the DOE and nuclear community are
very sensitive to.  For one particular scenario, the Cyclus results also
showed no fuel shortages for reactors, while the VISION results indicated
noticeable shortages.  This observation prompted a closer investigation to
determine if the differences were caused by mistakes in simulator input, bugs
in the simulator(s), or differing modeling choices between the simulators.
This investigation eventually developed into this work which shows important
effects of some modeling choices that are operative in many fuel cycle
simulators.

@@

@@

Raw data, custom code, instructions for reproducing results, and other
artifacts are available for download and use at
\url{http://dx.doi.org/10.6084/m9.figshare.1546775} \cite{Carlsen2015}.
